---
title: "Celebrity-Faceoff Dataset"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```


* [taken from jlacko github](https://github.com/jlacko/celebrity-faceoff)

The underlying dataset consits of 9,000 tweets, collected on 2019-02-02 via rtweet. It consists of 1,500 tweets each from

* Hadley Wickham,
* Wes McKinney,
* François Chollet,
* Kim Kardashian,
* Kourtney Kardashian,
* Khloe Kardashian

From each account 1,200 tweets (80%) are included in training dataset and 300 (20%) in verification set.

```{r, eval = T}
pacman::p_load(tidyverse)

tweets <- read_csv("train_tweets.csv") %>% 
  mutate(split = T) %>% 
  bind_rows(read_csv("test_tweets.csv")) %>% 
  mutate(split = ifelse(is.na(split), F, split)) %>%
  glimpse

tweets %>% count(split)
#save(tweets, file = "tweets.Rdata")
```

```{r}
celeb_mat <- tweets$name %>%
  dummies::dummy() 

celeb_names <- celeb_mat %>% 
  colnames %>% 
  str_remove("name|/Users/syro/MEGA/projects/celebrity-faceoff/code/keras_cnn.Rmd")

celeb_target <- celeb_mat %>% 
  as_tibble %>% 
  set_names(celeb_names) %>% 
  glimpse
```

```{r}
set.seed(2019)
text_train <- tweets %>% filter(split) %>% pull(text)
text_test <- tweets %>% filter(!split) %>% pull(text)
y_train <- celeb_target[tweets$split, ] %>% as.matrix
y_test <- celeb_target[!tweets$split, ] %>% as.matrix

celeb_dat <- list(
  text_train = text_train, 
  text_test = text_test, 
  y_train = y_train, 
  y_test = y_test
)

celeb_dat %>% glimpse
save(celeb_dat, file = "celeb_dat.Rdata")
```



# Old

* moved into the tuning process
* adds 2 new parameter

```{r, eval = F}
library(keras)
maxlen <- 60
max_features <- 13488

tokenizer <- text_tokenizer(num_words = max_features, lower = F, split = " ", char_level = F)
fit_text_tokenizer(tokenizer, train$text)

celeb$x_train <- tokenizer %>% 
  texts_to_sequences(train$text) %>%
  pad_sequences(maxlen = maxlen)

celeb$x_test <- tokenizer %>% 
  texts_to_sequences(test$text) %>%
  pad_sequences(maxlen = maxlen)

celeb %>% map(dim)
save(celeb, file = "celeb.Rdata")
```